---
output: github_document
---

```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
library(magrittr)
devtools::load_all()
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Repository

This is the repository for the analysis script of the paper *Does your past define you? The role of previous visual experience in predicting new affective pictures and sounds*. This folder allows to fully reproduce the analysis reported in the paper, and producing tables, figures and the supplementary materials.

# Folder's organization

The folder is organized as using `.Rprojects`, and all functions within the `R/` folder are automatically loaded in the global environment.

- `data/`: contains raw data for each experiment, both in `.rds` and `.csv` format
- `figures/`: contains all figures
- `tables/`: contains all tables
- `objects/`: contains all objects created by analysis scripts
- `R/`: contains all custom functions used in the project
- `script_visual/auditory`: contains all script to reproduce the analysis:
  - `*_outliers`: detect and remove relevant outliers
  - `*_analysis`: the main analysis reported in the paper
  - `*_exploratory`: extra analysis included in the supplementary materials
  - `*_paper_figures_tables`: create figures and tables
- `script_1vs2`: contains the analysis script for comparing experiment 1 vs experiment 2
- `supplementary`: contains the `.Rmd` file to create the supplementary materials in `.pdf` format
- `renv/`: contains the R environment with all packages version in order to reproduce the analysis
- `renv.lock`: contains all project dependencies
- `main_script.R`: is the main script that call each sub-script to run the full analysis

## Suggested workflow

1. Make sure that *R* and *Rstudio* are up-to-date. Under the *Session Info* section is reported the R version used for this project.
2. Install the [`renv`](https://rstudio.github.io/renv/articles/renv.html) package for managing dependencies
3. Open the `ConEmo12.Rproj` file
4. Use `renv::init()` in order to initialize the project with `renv`
5. Use `renv::restore()` in order to install packages from the `renv.lock` file
6. Run the `main_script.R` file. This script can be launched directly `source("main_script.R")` or each analysis step separately using `run_script()`.

In order to compile the `supplementary.Rmd` file is necessary to have `Latex` installed. Using the `tinytex` package ([link](https://yihui.org/tinytex/)) is possible to install a lightweight `Latex` distribution to compile `.Rmd` files.

# Dataset description

- `workerId`: unique identifier for each subject
- `group`: between-subject variable that identifies the experimental group (UG = uncertain group and CG = certain group)
- `cond`: relevant response required in each trial: exp = Expectancy rating, val_arr = Valence/Arousal rating
- `S1_color`: the color of the S1 stimulus (red and blue)
- `valence`: the valence of the S2 stimulus (Negative and Neutral)
- `Cong`: the S2 congruency: 0 = congruent (trials of the test phase in which the S1-S2 pairing was more likely, i.e., 75%), 1 = incongruent (trials of the test phase in which S1-S2 pairing was less likely, i.e., 25%)
- `exprating/valrating/arrating`: response variables: exprating = expectancy rating, valrating = valence rating, arrating = arousal rating

The dataset is organized in long format, where each line is a trial. The `cond` variable indicate which response variable is relevant for that specific trial.

# Packages

```{r results = 'asis', echo=FALSE}
get_all_packages() %>% cat(sep = "\n")
```

# Session Info

```{r}
session_info()
```